Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-06 talk/dls2012/paper.tex
address the prolog comment

\revb{
Section 7 also mentions performance improvements for a Prolog
interpreter. Consider adding a brief explanation of the benefit, since
that example stands out as a non-numeric (I assume) performance
improvement.
}

@@

Other interesting interpreters that are helped greatly by this
optimization are for
example our Prolog interpreter written in RPython, as well as numerical
kernel used for array manipulation. The exact extent is out of scope for
this paper.

>>>>

@@

Other interesting interpreters that are helped greatly by this optimization are
for example our Prolog interpreter written in RPython
\cite{carl_friedrich_bolz_towards_2010}. Prolog programs often contain tight
loops that perform list processing. Furthermore we experimented with a language
for writing numerical kernel used for array manipulation. The exact extent is
out of scope for this paper.
